---
title: "Solve the knapsack problem with different methods"
author: "Anton Persson & Emil Klasson Svensson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Lab6 is a package created during a R programming course given by Linkoping University. 
The package includes three functions which provides three different methos to solve the knapsack problem, with different computational complexity. The three methods are brute force, dynamic and greedy.

## Package Info
The user of each of the three functions are supposed to use a data frame with two variables, w och v, and an integer W as input. The data frame should contain the actual data, and W is the maximum weigth the knapsack can bear. 
These inputs will return a list with the maximum value and the chosen items given by the algorithm.


## Examples of how to use the lab6 package

### knapsack_brute_force 

To use brute force to solve the knapsack problem, use the brute\_force function that is included in the package. This method guarantee that you\'ll get the correct answer.

```{r, echo=TRUE, message = FALSE, warning = FALSE }
library(Lab6)

##Building a dataset to test on
set.seed(42)
n <- 2000 

knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE), 
                                v=runif(n = n, 0, 10000) )

##Use the the first 16 rows of data, and W=2000
knapsack_brute_force(x = knapsack_objects[1:12,], W=2000) 

##You might wonder how heavy brute force is. Let's see!
system.time(knapsack_brute_force(x = knapsack_objects[1:16,], W=2000))

```


### knapsack_dynamic

If you want a faster solution to the problem, you can use the knapsack\_dynamic function instead. 

```{r, echo=TRUE, message = FALSE, warning = FALSE }
##Use the the first 12 rows of data, and W=2000
knapsack_dynamic(x=knapsack_objects[1:12,], W=2000)



## How long time does it takes to run the algorithm for n = 500 objects!
system.time(knapsack_dynamic(x=knapsack_objects[1:500,], W=2000))

```

The knapsack\_dynamic function is clearly faster than the brute force. Notice that 500 rows are investigated in this case, compared to 16 in the brute force example.

### knapsack_greedy

Finally, let\'s use the greedy heuristic. This algorithm is an approximation, i.e. it won\'t guarantee the correct answer. Instead, it\'s supposed to be really fast!

```{r, echo=TRUE, message = FALSE, warning = FALSE }
##Use the the first 800 rows of data, and W=3500
knapsack_greedy(x = knapsack_objects[1:800,], W = 3500)


## How long time does it takes to run the algorithm for n = 1000000 objects?
set.seed(42)
n <- 1000000 

knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE), 
                                v=runif(n = n, 0, 10000) )
system.time(knapsack_greedy(x = knapsack_objects[1:1000000,], W = 3500))

```

The knapsack\_greedy function works faster than the previous algorithms, which is shown above. Notice that we in this case runs over a million observations. That wouldn't be possible in the brute force function.


##Contact info

If you find any problems with the package or it\'s documentation, please send us some feedback or critique. Contact Anton Persson, antpe404@student.liu.se, or Emil Klasson Svensson, emisv463@student.liu.se.
